%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Full Stack Developer} % Job title
    %{Dunamu Inc.} % Organization
    {Canada} % Location
    {2021 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {3+ years of experience as a self-taught full-stack web developer with a passion for creating user-friendly and responsive websites that meet the needs of users. Proficient in a wide range of technologies including HTML, CSS, JavaScript, React, NextJS, Node.js, PHP - Laravel, and Python.}
        \item {Skilled in both front-end and back-end development, with a strong understanding of web architecture and best practices. Experienced in working with agile methodologies and collaborating with cross-functional teams to deliver high-quality software products.}
        \item {Eager to learn new technologies and stay up-to-date with the latest trends in web development. Committed to delivering exceptional results and exceeding expectations.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Bachelors of Economics} % Job title
    {University of New Brunswick} % Organization
    {Fredericton, NB, Canada} % Location
    {2019 - 2020} % Date(s)
    {
     % \begin{cvitems} % Description(s) of tasks/responsibilities
      %  \item {Was not allowed to attend university/'higher eduKSean' because I refused to take an untested so called medication because the TV/Govt/Big Phama told me to, If you are so smart - why are you taking god knows what mystery $cience juice?}
      %  \item {I saved 40k/a year by not paying for my own indoctrinateSean, and getting my special piece of paper that says I am competent. While listening to so called teachers read verbatim powerpoints for 4 years telling me how smart I am for wasting 4 years, and 100's of thousands of dollars on my special piece of paper. }
      %  \item {Also didn't waste time listening to govt funded so called schools, tell me how 'keynes was right - deficit spending gud - more spending - more taxes, muh central banks muh interest rates, green line go up!'}
      %  \item {Established a standardized base for declarative management of infrastructures and service deployments, enabling operational efficiency and consistency. Over 90\% of AWS resources were all managed through standardized terraform modules. All add-ons and service workloads on the Kubernetes cluster were managed on a GitOps basis with Kustomize and ArgoCD.}
      %  \item {Saved over 30\% of the overall AWS costs by establishing a quarterly purchasing strategiy for RI (Reserved Instance) and SP (Savings Plan) and by introducing Graviton instances.}
      %  \item {Established a core architecture for regulating of outbound DNS traffic in multi-account and multi-VPC environments utilizing AWS Route53 DNS Firewall and FMS. This significantly increased the level of security confidence in the financial sector's segregated environment.}
      %  \item {Introduced Okta employee identity solution in the company, establishing security policies and configuring SSO integration with over 20 enterprise systems including AWS, GitHub, Slack, Google Workspace. Set up a Hub and Spoke architecture, enabling a collaborative account structure with the parent company, Daangn Market.}
     % \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Senior English Teacher / Manager} % Job title
    {Shane English} % Organization
    {Yangzhou, China} % Location
    {2016 - 2019} % Date(s)
    {
      \begin{cvitems}
        \item {Curriculum Development: Expertise in designing and implementing comprehensive English language curricula aligned with international standards and best practices.}
        \item {Instructional Delivery: Skilled in delivering dynamic and interactive lessons that incorporate a variety of teaching methodologies, including communicative language teaching, task-based learning, and technology integration.}
        \item {Successfully led a team of English teachers, providing guidance, support, and professional development opportunities. Monitored teacher performance and provided constructive feedback to help them improve their teaching skills and effectiveness.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Landscaper} % Job title
    {Fredericton Landscaping} % Organization
    {Fredericton, NB, Canada} % Location
    {2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Excellent communication and interpersonal skills, fostering positive relationships with clients and colleagues.}
        \item {Successfully managed a team of 3 landscapers, ensuring efficient and productive work practices.}
        \item {Proactively identified and resolved potential landscape issues, preventing costly repairs.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Apprentice Plumber} % Job title
    {Mystique Mechanical} % Organization
    {Calgary, AB, Canada} % Location
    {2014} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Completed plumbing projects on time and within budget, exceeding client expectations.}
        \item {Adaptable and able to work independently or as part of a team.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {ACP-EMT-Medic MOS ID 00334} % Job title
    {DoD- Canadian Forces} % Organization
    {Canada} % Location
    {2009-2013} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Highly motivated and results-oriented ACP-EMT-Medic with 4+ years of experience in providing emergency medical care in diverse military settings.}
        \item {Proven ability to assess and treat patients with a wide range of injuries and illnesses, ensuring their safety and well-being. In both a clinical and field ambulance settings.}
        \item {Skilled in administering medications, performing advanced medical procedures, and operating medical equipment.}
        \item {Strong knowledge of medical protocols and procedures, ensuring adherence to best practices and patient safety.}
        \item {Excellent communication and interpersonal skills, fostering trust and rapport with patients and colleagues.}
        \item {Maintained accurate and complete electronic medical records (EMRs), ensuring patient confidentiality and data integrity. Adhered to HIPAA regulations and best practices for data security and privacy.}
        \item {Utilized EMR systems to document patient encounters, track medications, and monitor health conditions. As well as secure funding and reschedule clinical appointments and treatments.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Grocery} % Job title
    {Sobeys} % Organization
    {Fredericton, NB, Canada} % Location
    {2008-2009} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Responsible for transportation and distribution of stock. Management and processing of stock in a warehouse environment.}
        \item {Proactively identified and addressed potential stock issues, preventing product shortages and ensuring customer satisfaction.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
